---
title: "final article"
author: "Leo"
date: '2022-07-02'
output: 
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# First include basic settings and related packages.
```{r,echo=TRUE,prompt=TRUE,message=FALSE}
library(tidyverse)
library(skimr)
library(MASS)
library(openxlsx)
library(pander)
library(ggplot2)
library(Rcpp)
library(dplyr)
library(forcats)
library(hrbrthemes)
library(viridis)
```

******

# Read and roughly view data 'article data' in project's working directory
```{r,echo=TRUE,prompt=TRUE}
rawdata <- read.xlsx("article data.xlsx")
head(rawdata)
skim(rawdata)
```

******

# Data EDA

## Age and gender distribution of different types of alopecia
```{r,echo=TRUE,prompt=TRUE}
alopecia_data <- rawdata[grep(pattern="1",rawdata$ALOPECIA),]
alopecia_data%>%
  ggplot(aes(x = TYPE,y = AGE))+
  geom_violin(aes(fill = GENDER),trim = FALSE,alpha = 0.5)+
  scale_fill_manual(values = c("#58B2DC","#0089A7"))+
  xlab("Alopecia type")+
  ylab("Age(Year)")+
  ylim(0,100)+
  ggtitle("Violin plot of age in different type of alopecia") +
  theme_classic()
```

******
# Age and level of alopecia
## AGA part
## ## 1st. Divide data into two groups via gender and delete col with NA
```{r,echo=TRUE,prompt=TRUE}
aga_data <- alopecia_data[grep(pattern = "AGA",alopecia_data$TYPE),]
agamale_data <- aga_data[grep(pattern="Male",aga_data$GENDER),]
agamale_data <- agamale_data[,-c(6,7,8)]
agafemale_data <- aga_data[grep(pattern="Female",aga_data$GENDER),]
agafemale_data <- agafemale_data[,-c(5,7,8)]
```

******

## 2nd. Conduct some EDA
### Point and line plot of AGA level against AGE.YEARS
```{r,echo=TRUE,prompt=TRUE}
agamale_data%>%
  ggplot(mapping = aes(x = AGE,y = HNS)) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Relationship between AGA level(HNS) and 
          Patients' age in male")
agafemale_data%>%
  ggplot(mapping = aes(x = AGE,y = LS)) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Relationship between AGA level(LS) and 
          Patients' age in female")
```

******

## 3rd. Fit a linear regression model to explain the AGA level
```{r,echo=TRUE,prompt=TRUE}
full.model1 <- lm(HNS ~ AGE,data = agamale_data)
summary(full.model1)
full.model2 <- lm(LS ~ AGE,data = agafemale_data)
summary(full.model2)
```

******

## 4th. Variable Selection(only one variable maybe meaningless)
```{r,echo=TRUE,prompt=TRUE}
stepwiseSelection1 <- stepAIC(full.model1,direction = "both",
                              trace = FALSE,k = log(NROW(agamale_data)))
summary(stepwiseSelection1)
pander::pander(stepwiseSelection1)
stepwiseSelection2 <- stepAIC(full.model2,direction = "both",
                             trace = FALSE,k = log(NROW(agafemale_data)))
summary(stepwiseSelection2)
pander::pander(stepwiseSelection2)
```

******

## 5th. Interpretation
$$
\hat{HNS(male)} = 0.957 + 0.0468 * AGE
$$
## 6th. Draw a plot
```{r,echo=TRUE,prompt=TRUE}
agamale_data%>%
  ggplot(aes(x = AGE,y = HNS))+ 
  geom_point(colour = "black",size = 0.7,alpha = 0.7)+
  geom_smooth(method = lm, color = "#58B2DC",fill = "#69b3a2",se = TRUE)+
  xlab("Age of male patient")+
  ylab("Level of AGA(HNS)")
```

******

## AA part
## ## 1st. Divide data into two groups via gender and delete col with NA
```{r,echo=TRUE,prompt=TRUE}
aa_data <- alopecia_data[grep(pattern = "AA",alopecia_data$TYPE),]
aa_data <- aa_data[,-c(5,6,8)]
```

******

## 2nd. Conduct some EDA
### Point and line plot of AGA level against AGE.YEARS
```{r,echo=TRUE,prompt=TRUE}
aa_data%>%
  ggplot(mapping = aes(x = AGE,y = SALT)) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Relationship between AA level(SALT) and 
          Patients' age")
```

******

## 3rd. Fit a linear regression model to explain the AGA level
```{r,echo=TRUE,prompt=TRUE}
full.model3 <- lm(SALT ~ AGE,data = aa_data)
summary(full.model3)
```

******

## 4th. Variable Selection(only one variable maybe meaningless)
```{r,echo=TRUE,prompt=TRUE}
stepwiseSelection3 <- stepAIC(full.model3,direction = "both",
                              trace = FALSE,k = log(NROW(aa_data)))
summary(stepwiseSelection3)
pander::pander(stepwiseSelection3)
```

******

## TE part
## ## 1st. Divide data into two groups via gender and delete col with NA
```{r,echo=TRUE,prompt=TRUE}
te_data <- alopecia_data[grep(pattern = "TE",alopecia_data$TYPE),]
te_data <- te_data[,-c(5,6,7)]
```

******

## 2nd. Conduct some EDA
### Point and line plot of AGA level against AGE.YEARS
```{r,echo=TRUE,prompt=TRUE}
te_data%>%
  ggplot(mapping = aes(x = AGE,y = RESOLUTION)) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Relationship between TE level(RESOLUTION) and 
          Patients' age")
```

******

## 3rd. Fit a linear regression model to explain the AGA level
```{r,echo=TRUE,prompt=TRUE}
full.model4 <- lm(RESOLUTION ~ AGE,data = te_data)
summary(full.model4)
```

******

## 4th. Variable Selection(only one variable maybe meaningless)
```{r,echo=TRUE,prompt=TRUE}
stepwiseSelection4 <- stepAIC(full.model4,direction = "both",
                              trace = FALSE,k = log(NROW(te_data)))
summary(stepwiseSelection4)
pander::pander(stepwiseSelection4)
```

******

# Age and alopecia logist
```{r,echo=TRUE,prompt=TRUE}
age_logit <- glm(ALOPECIA ~ AGE + GENDER,data = rawdata, family = "binomial")
summary(age_logit)
```

******

# Gender and alopecia chisq.test
```{r,echo=TRUE,prompt=TRUE}
gender_data <- rawdata[,-c(2,5,6,7,8,9)]
gender_data$GENDER[gender_data$GENDER == "Female"] = 1
gender_data$GENDER[gender_data$GENDER == "Male"] = 0
aga_gdata <- gender_data[grep(pattern = "GA",gender_data$TYPE),]
aa_gdata <- gender_data[grep(pattern = "AA",gender_data$TYPE),]
te_gdata <- gender_data[grep(pattern = "TE",gender_data$TYPE),]
aga_gdata <- table(aga_gdata$GENDER,aga_gdata$ALOPECIA)
aa_gdata <- table(aa_gdata$GENDER,aa_gdata$ALOPECIA)
te_gdata <- table(te_gdata$GENDER,te_gdata$ALOPECIA)
aga_gdata
aa_gdata
chisq.test(aga_gdata)
chisq.test(aa_gdata)
```