---
title: "Final project"
author: "Leo"
date: '11/06/22'
output: 
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# First include basic settings and related packages.
```{r,echo=TRUE,prompt=TRUE,message=FALSE}
library(tidyverse)
library(skimr)
library(MASS)
library(openxlsx)
library(pander)
```

# Read and roughly view data 'JAAD RAW DATA' in project's working directory
```{r,echo=TRUE,prompt=TRUE}
rawdata <- read.xlsx("JAAD RAW DATA.xlsx")
head(rawdata)
skim(rawdata)
```

******

# Effect of age on AGA level in male or female
## 1st. Divide data into two groups via gender and delete col with NA
```{r,echo=TRUE,prompt=TRUE}
male_data <- rawdata[grep(pattern="0",rawdata$FEMALE),]
male_data <- male_data[grep(pattern="1",male_data$AGA),]
male_data <- male_data[,-5]
female_data <- rawdata[grep(pattern="1",rawdata$FEMALE),]
female_data <- female_data[grep(pattern="1",female_data$AGA),]
female_data <- female_data[,-4]
```

******

## 2nd. Conduct some EDA
### Point and line plot of AGA level against AGE.YEARS
```{r,echo=TRUE,prompt=TRUE}
male_data%>%
  ggplot(mapping = aes(x = AGE.YEARS,y = NHS)) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Relationship between AGA level(NHS) and 
          Patients' age in male")
female_data%>%
  ggplot(mapping = aes(x = AGE.YEARS,y = LS)) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Relationship between AGA level(LS) and 
          Patients' age in female")
```

******

## 3rd. Fit a linear regression model to explain the AGA level
```{r,echo=TRUE,prompt=TRUE}
full.model1 <- lm(NHS ~ .,data = male_data)
summary(full.model1)
full.model2 <- lm(LS ~ .,data = female_data)
summary(full.model2)
```

******

## 4th. Variable Selection(only one variable maybe meaningless)
```{r,echo=TRUE,prompt=TRUE}
stepwiseSelection1 <- stepAIC(full.model1,direction = "both",
                              trace = FALSE,k = log(NROW(male_data)))
summary(stepwiseSelection1)
pander::pander(stepwiseSelection1)
stepwiseSelection2 <- stepAIC(full.model2,direction = "both",
                             trace = FALSE,k = log(NROW(female_data)))
summary(stepwiseSelection2)
pander::pander(stepwiseSelection2)
```

******

## 5th. Interpretation
$$
\hat{NHS(male)} = 1.631 + 0.0378 * AGE.YEARS
$$

### Keep other covariates unchanged, the NHS of male is expected to increase by 0.0378 with every unit increase of AGE.YEARS.

### By fitting models, we discovered that there is little correlation between level of AGA(LS) and AGE.YEARS in female.(Maybe it's because the female sample is too small)

******

# Effect of gender on AGA(T-test)
## Conduct some EDA
### Bar plot of AGA level against gender
```{r,echo=TRUE,prompt=TRUE}
AGA_data <- rawdata[grep(pattern="1",rawdata$AGA),]
combine_data <- AGA_data%>%
  pivot_longer(c(NHS,LS),names_to = "GENDER.TYPE",values_to = "AGA.level")
combine_data <- na.omit(combine_data)
colorset <- c("#58B2DC","#0089A7")
combine_data%>%
  group_by(GENDER.TYPE) %>%
  summarise(n = n(), AGA.level = mean(AGA.level)) %>%
  ggplot(aes(x = GENDER.TYPE, y = AGA.level, fill = GENDER.TYPE)) + geom_bar(stat = "identity") + 
  ggtitle("Bar plot of AGA level against gender") + 
  scale_fill_manual(values = colorset)
```

******

## Delete cols including NA and conduct T-test
```{r,echo=TRUE,prompt=TRUE}
gender_data <- rawdata[,-c(4,5)]
ttest<- t.test(gender_data$AGA~gender_data$FEMALE)
pander::pander(ttest)
```

******
## Discovery
### T-test shows that p is less than 0.01, which means there is true differences between male and female in AGA. So the effect of gender on AGA is considerable.