---
title: "Homework-4"
author: "Leo"
date: '17/05/2022'
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# First include basic settings and related packages.
```{r,echo=TRUE,prompt=TRUE,message=FALSE}
library(tidyverse)
library(skimr)
library(MASS)
```

******

# Data analysis with dataset 'bridge.txt'

## 1st. read data 'bridge.txt' in project's working directory
```{r,echo=TRUE,prompt=TRUE}
bridge <- read.table("bridge.txt",header = T)
head(bridge)
skim(bridge)
```

******

## 2nd. Delete the variable ‘Case’ and transform all the variables to the log form
```{r,echo=TRUE,prompt=TRUE}
bridge <- bridge[,-1]
bridge <- log(bridge)
head(bridge)
```

******

## 3rd. EDA examples
```{r,echo=TRUE,prompt=TRUE}
#Concerning design time of a bridge, I prefer Numbers of structural drawings to be more relevant. First let's conduct an EDA.
bridge%>%
  ggplot(mapping = aes(x = Dwgs,y = Time)) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Relationship between Design time of a bridge and 
          Numbers of structural drawings")
```

******

## 4th. Fit a linear regression model to explain the Design time of a bridge
```{r,echo=TRUE,prompt=TRUE}
#Construct the full linear regression model using Time as the response variable
full.model <- lm(Time ~ .,data = bridge)
summary(full.model)
```

******

## 5th. Variable Selection(Backward Selection)
```{r,echo=TRUE,prompt=TRUE}
#Using stepwise selection with BIC
stepwiseSelection <- stepAIC(full.model,direction = "both",
                             trace = FALSE,k = log(NROW(bridge)))
summary(stepwiseSelection)
```

## 6th. Interpretation
$$
\hat{log(Time)} = 2.66 + 1.04 * log(Dwgs) + 0.29 * log(Spans)
$$

### 1.Keep other covariates unchanged, the log(Time) is expected to increase by 1.04% with every unit increase of log(Dwgs).

### 2.Keep other covariates unchanged, the log(Time) is expected to increase by 0.29% with every unit increase of log(Spans).