---
title: "Homework-5 groupwork"
author: "Leo, Jack and Yefei Cui"
date: '2022-05-24'
output: 
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# First include basic settings and related packages.
```{r,echo=TRUE,prompt=TRUE,message=FALSE}
library(tidyverse)
library(skimr)
library(MASS)
library(ISLR)
library(fpp2)
library(forecast)
library(tseries)
library(Metrics)
library(ggplot2)
```

******

# 0.Read dataset 'monthly-sunspots' in the work directory and transform it into time series set
```{r,echo=TRUE,prompt=TRUE}
sunspots <- read.csv("monthly-sunspots.csv")
sunspots <- ts(sunspots$Sunspots,frequency = 12,start = c(1749,1), end = c(1983,12))
train_sunspots <- window(sunspots,start = c(1749,1), end = c(1937,12))
test_sunspots <- window(sunspots,start = c(1938,1), end = c(1983,12))
```

******

# 1.Conduct some EDA
```{r,echo=TRUE,prompt=TRUE}
# EDA with whole data
head(sunspots)
summary(sunspots)
plot.ts(sunspots)
```

```{r,echo=TRUE,prompt=TRUE}
# EDA with training part and testing part to predict
predict_meanf <- meanf(train_sunspots,h = 12)
rmse(test_sunspots,predict_meanf$mean)

predict_naive <- naive(train_sunspots,h = 12)
rmse(predict_naive$mean,test_sunspots)

predict_snaive <- snaive(train_sunspots,h = 12)
rmse(predict_snaive$mean,test_sunspots)

predict_rwf <- rwf(train_sunspots,h = 12)
rmse(predict_rwf$mean,test_sunspots)

predict_ses <- ses(train_sunspots,h = 12)
rmse(predict_ses$mean,test_sunspots)
```

```{r,echo=TRUE,prompt=TRUE}
#EDA with ggplot2
autoplot(sunspots) + geom_forecast(colour = "lightblue")
```

******

# 2.Decompose the data
```{r,echo = TRUE,prompt=TRUE}
dec_sunspots <- decompose(sunspots)
Res <- dec_sunspots$Sunspots
plot(dec_sunspots)
```

## We can observe from the plot that the data has a strong seasonal pattern. But we think the random noise is too big so we try to adjust our plot.

```{r,echo=TRUE,prompt=TRUE}
dec_sunspotsadjusted <- sunspots - dec_sunspots$random
plot(dec_sunspotsadjusted)
```

## As is shown, the plot is much smoother without random noise. But we can still find some jumps in several periods.

******

# 3.Test data
```{r,echo=TRUE,prompt=TRUE}
adf.test(sunspots)
```
## We can see that p value is smaller than 0.01, which means our data is very stationary.
```{r,echo=TRUE,prompt=TRUE}
ndiffs(sunspots)
```
## Because k > 0 and k = 1, so we need to use first difference to conduct a stantionary data.
```{r,echo=TRUE,prompt=TRUE}
adf.test(diff(sunspots))
```
## Actually both initial data and first difference data are stationary enough.

******

# 4.Fit ARMA models
## First fit initial data
```{r,echo=TRUE,prompt=TRUE}
arma_model1 <- arima(sunspots, order = c(1, 0, 1))
arma_model1
lmtest::coeftest(arma_model1)
arma_model2 <- arima(sunspots, order = c(4, 0, 3))
arma_model2
lmtest::coeftest(arma_model2)
arma_model3 <- arima(sunspots, order = c(2, 0, 2))
arma_model3
lmtest::coeftest(arma_model3)
```
### We can see that concerning AIC(If AIC is smaller, it's better), (4,0,3) is the best type of selected models

## Then try to fit first difference data
```{r,echo=TRUE,prompt=TRUE}
sunspots %>%
  diff() %>%
  arima(order = c(1,1,1)) %>%
  lmtest::coeftest()
sunspots %>%
  diff() %>%
  arima(order = c(4,1,3)) %>%
  lmtest::coeftest()
sunspots %>%
  diff() %>%
  arima(order = c(2,1,2)) %>%
  lmtest::coeftest()
```

## Use auto.arima to select model
```{r,echo=TRUE,prompt=TRUE}
sunspots %>%
  auto.arima() %>%
  summary()
sunspots %>%
  auto.arima() %>%
  lmtest::coeftest()
```

## We can see that (2,1,2) is the best of all model types to fit in

******

# 5.Roles of our group
## Leo: Extra EDA part and some decomposition parts.
## Jack: ts.plot, EDA.
## Yefei Cui: EDA and ARIMA model.
## We mainly discussed online through wechat, and exchanged our thoughts about coding and some problems, and leo helped explain some definitions.